### 2015-06-26 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Removed unnecessary drawing files and finished folder organization

\input{../../../../Bibliography/commoncommands}

@@

\flushright{
\includegraphics[width=2.in]{../../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/hose_streams.pdf}
\caption[Different Hose Stream Patterns]{The three types of hose stream patterns, straight stream (left), narrow fog stream (middle), and wide fog stream (right), used during the water flow experiments.}
\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/east_structure}
\\~\\
\includegraphics[width=6in]{../../Figures/west_structure}
\caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
\label{fig:west_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
\caption[Location of Instrumentation in West Structure]{Location of Instrumentation in West Structure}
\label{fig:west_instrumentation}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/BDPs}
\caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
\label{fig:BDPs}
\end{figure}

@@

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor with a combination nozzle. A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}). After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This process was repeated an additional time.

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A13_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A13_Avg_All}
\end{figure}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A13_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A13_Avg_All}
\end{figure}

>>>>

\input{../../../../../Bibliography/commoncommands}

@@

\flushright{
\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
\caption[Different Hose Stream Patterns]{The three types of hose stream patterns used during the water flow experiments from left to right: straight stream, narrow fog stream, and wide fog stream.}
\label{fig:hose_streams}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/east_structure}
\\~\\
\includegraphics[width=6in]{../Pictures/west_structure}
\caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
\caption[East Structure floor layout]{East Structure floor layout. All dimensions are in meters.}
\label{fig:east_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
\label{fig:west_general_plan}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.25cm 3.75cm, clip=true, width=6in]{../Drawings/Instrumentation/East_Structure_Devices_Hose_Test}
\caption[Location of Instrumentation in East Structure]{Location of instrumentation in East Structure}
\label{fig:east_instrumentation}
\end{figure}

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
\caption[Location of Instrumentation in West Structure]{Location of instrumentation in West Structure}
\label{fig:west_instrumentation}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/BDPs}
\caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
\label{fig:BDPs}
\end{figure}

@@

Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor equipped with a combination nozzle. A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30. Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}). After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped. The monitor was adjusted so the nozzle was aimed at Door BC. Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped. This process was repeated an additional time.

@@

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18. Both double doors and the south side door on the first floor were in the opened position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_1}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
\\
\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19. Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test. On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
\label{fig:flow_path_2}
\end{figure}
\FloatBarrier

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/Test_18}
\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18. A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
\label{fig:test_18_pic}
\end{figure}
\FloatBarrier

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
\label{fig:Test_16_BDP_A13_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
\label{fig:Test_17_BDP_A13_Avg_All}
\end{figure}

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
\\
\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
\midrule
\textit{Straight} & 
%%%%Test 16%%%% 
0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
%%%%Test 17%%%% 
0.7 $\pm 0.1$ & 0.7 $\pm 0.2$
\\	\multicolumn{5}{c}{}	\\
\textit{Narrow Fog} & 
%%%%Test 16%%%% 
1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $          
\\	\multicolumn{5}{c}{}	\\
\textit{Wide Fog} 	& 
%%%%Test 16%%%% 
1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
%%%%Test 17%%%% 
0.9 $\pm 0.2$ & 0.7 $\pm 0.2$
\\
\bottomrule
\end{tabular}
\label{table:Tests_16_17_BDP_A10_Avgs}
\end{table}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
\label{fig:Test_18_BDP_A13_Avg_All}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A10_Avg_All}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
\label{fig:Test_19_BDP_A13_Avg_All}
\end{figure}
